---
title: "Bank_Marketing"
author: "H"
date: "10/15/2021"
output: html_document
---


## Import data
```{r}
conversionDF <- read.csv('bank-additional-full.csv', header = TRUE, sep = ";")

```
# Encode conversion as 0s and 1s 
# Output variable y = has information on whether a client has subscribed to a term deposit, encoded 'yes' or 'no'
```{r}
conversionDF$conversion <- ifelse(conversionDF$y== "yes",1, 0)

```

# check the data
```{r}
head(conversionDF,50)
str(conversionDF)
```

# Aggregate conversion rate 

# Total number of conversions
```{r}
sum(conversionDF$conversion)

```
# Total number of clients in the data (number of record of data)
```{r}
nrow(conversionDF)

```
```{r}
sprintf("Total conversions: %i out of %i", sum(conversionDF$conversion),nrow(conversionDF))
```
```{r}
sprintf("Total conversion rate : %0.2f%%", sum(conversionDF$conversion)/nrow(conversionDF)*100)

```
# Conversion rates by age
```{r}
library(dplyr)
```
### Group by age and count each age group using n(), sum conversion for each age group and calculate conversionrate
```{r}
conversionsByAge <- conversionDF %>% group_by(Age=age) %>% summarise(TotalCount=n(), NumCoversions= sum(conversion)) %>% mutate(ConversionRate= NumCoversions/TotalCount*100.0) 
```
```{r}
head(conversionsByAge, 30)
```
### Line Chart
```{r}
library(ggplot2)
```
```{r}
ggplot(aes(x= Age, y= ConversionRate), data = conversionsByAge) +geom_line()+ ggtitle('Conversion By Age') + xlab("Age") +ylab("ConversionRate {%}") + theme(plot.title = element_text(hjust = 0.5))
```
# Grouping Age
```{r}
conversionsByAgeGroup <- conversionDF %>% group_by(AgeGroup= cut(age, breaks = seq(20,70, by=10))) %>% summarise (Totalcount =n(), Numconversions= sum(conversion)) %>% mutate(conversionRate = Numconversions/ Totalcount *100)
```
```{r}
head(conversionsByAgeGroup)
```
```{r}
conversionsByAgeGroup$AgeGroup <- as.character(conversionsByAgeGroup$AgeGroup)
```
```{r}
conversionsByAgeGroup$AgeGroup[6] <- "70+"
```


# Bar Chart 
```{r}
ggplot(aes(x= AgeGroup, y = conversionRate), data = conversionsByAgeGroup) + geom_bar(width = 0.5, stat = 'identity')+ ggtitle('Conversion By AgeGroup') + xlab("Age") +ylab("ConversionRate {%}") + theme(plot.title = element_text(hjust = 0.5))
```
# Conversions vs non-conversions
```{r}
conversionsByMaritalStatus <- conversionDF %>% group_by (Marital = marital, Conversion = conversion) %>% summarise(Count = n(),.groups = 'drop')

```


```{r}
head(conversionsByMaritalStatus)
```
## Pie chart 
```{r}
ggplot(aes(x= "", y = Count, fill =Marital),data = conversionsByMaritalStatus) + 
  geom_bar(width = 1, stat = "identity", position = position_fill()) +
  geom_text(aes(x = 1.25, label = Count), position = position_fill(vjust = 0.5)) +
  coord_polar("y") +
  facet_wrap(~Conversion)+
  ggtitle("Marital Status (0: Nonconversions, 1: Conversions)") +
  theme(
    axis.title.x= element_blank(),
    axis.title.y =element_blank(),
    plot.title = element_text(hjust = 0.5),
    legend.position ="bottom"
  )

```
## Conversion by age and Marital Status 
```{r}
 conversionByAgeandMarital <- conversionDF %>% group_by(AgeGroup = cut(age, breaks =  seq(20, 70, by =10)), Marital=marital,) %>% 
  summarise(Count = n(), NumConversions = sum(conversion)) %>% 
  mutate(TotalCount = sum(Count)) %>% mutate(ConversionRate = NumConversions/TotalCount)
```

```{r}
str(conversionByAgeandMarital)
head(conversionByAgeandMarital, 20)
```
```{r}
conversionByAgeandMarital$AgeGroup <- as.character(conversionByAgeandMarital$AgeGroup)
conversionByAgeandMarital$AgeGroup[is.na(conversionByAgeandMarital$AgeGroup)] <- "70+"
```
```{r}
head(conversionByAgeandMarital, 60)
```

## Bar chart
```{r}
ggplot(aes(x= AgeGroup, y= ConversionRate, Fill =Marital), data = conversionByAgeandMarital) +geom_bar(width =  0.5, stat = "identity",
                                                                                                       position = "dodge")+
  ylab("Conversion Rate (%)") +
  xlab("Age")+
  ggtitle("Conversion Rate by Age and Marital Status")+ theme(plot.title = element_text(hjust = 0.5))
```
## Staced Bar Chart 
```{r}
ggplot(conversionByAgeandMarital,aes(x =AgeGroup, y= ConversionRate, Fill= Marital)) +geom_bar(aes(fill = Marital), stat = "identity")+
  ylab("Conversion Rate (%)") +
  xlab("Age")+
  ggtitle("Conversion Rate by Age and Marital Status")+ theme(plot.title = element_text(hjust = 0.5))
```

