---
title: "decisionTree"
author: "H"
date: "10/30/2021"
output: html_document
---


# Decision Tree 
## Conversion Rate : subscribe to a term deposit

```{r}
df <- read.csv('bank-additional-full.csv', header = TRUE, sep = ";")

```
# Encode conversion as 0s and 1s 
```{r}
df$conversion <- ifelse(df$y== "yes",1, 0)

```
```{r}
head(df, 100)
```
```{r}

```

```{r}
sprintf("Conversion Rate: %0.2f%%",sum(df$conversion)/nrow(df)*100)
```

```{r}
library(dplyr)
```
## Conversion rate by job
```{r}
conversionsByJob <- df %>% group_by(Job = job) %>% summarise(Count= n(), numConversion = sum(conversion)) %>% 
  mutate(ConversionRate = numConversion/Count *100.0)
```
```{r}
head(conversionsByJob, 40)
```

## Horizontal bar chart 
```{r}
library(ggplot2)
```
```{r}
ggplot( aes(x =Job, y= ConversionRate),data = conversionsByJob) +geom_bar(width = 0.5, stat = "identity") + coord_flip() + ggtitle("Conversiton Rate By Job") + xlab("Job")+ ylab("Conversion Rate (%)") +  theme(plot.title = element_text(hjust = 0.5))

```
### Student and Retired group have most highest conversion rate , Blue collar and service group have the lowest conversion rate 

## Defalut rate by conversion 
```{r}
DefaultByConversion <- df %>% group_by(Default = default, Conversion= conversion) %>% summarise(Count =n())
```
```{r}
head(DefaultByConversion, 10)
```
```{r}
 ggplot( aes(x ="", y= Count, fill= Default) ,data = DefaultByConversion) +geom_bar(width = 1 , stat = 'identity', position = position_fill())+
  coord_polar("y") +  facet_wrap(~Conversion)+ geom_text(aes(x = 1.25, label =Count), position = position_fill(vjust = 0.5)) +
  ggtitle("Default (Non Conversions :0 , Conversions :1 )")

```
##Coversion Rate by number of contacts

```{r}
ConversionByNumContact <- df %>% group_by(Campaign = campaign) %>% summarise(Count = n(), NumConversion = sum (conversion)) %>% 
  mutate(ConversionRate = NumConversion /Count *100)
```

```{r}
head(ConversionByNumContact, 10)
```
## Bar chart Conversion Rate by number of contact 
```{r}
ggplot( aes(x = Campaign, y = ConversionRate), data = ConversionByNumContact)+geom_bar(width = 0.5, stat = "identity") +
  ggtitle("Conversion Rate by Number of Contacts") +xlab("Number of Contacts") +ylab("Conversion Rate(%)") +
  theme(plot.title = element_text(hjust = 0.5))

```
### there is outlier in this bar chart, however, overall we can see the higher contacts decrease conversion rate.

## Encoding Categorical Variables
### * Encode month 
```{r}
unique(df$month)
```
```{r}
months =lapply(month.abb, function(x) tolower(x) )
df$month <- match(df$month,months)
```

## First, in month.add is built in R for month name with capital letter. Use Function to convert lower case 
## Then, use match function to convert the string value 

```{r}
df%>% group_by(month) %>% summarise(Count =n())
```
## Encoding the Job, Housing, Marital variables 
```{r}
df$job <- factor(df$job)
df$housing <- factor(df$housing)
df$marital <- factor(df$marital)
```

## Building Decision Trees 
```{r}
library(rpart)
```
```{r}
fit <- rpart(
  conversion ~ age +campaign + previous + housing + job +marital, method = "class", data =  df, control = rpart.control(maxdepth = 4, cp= 0.0001))
)
```
### aforemnetioned variables as the feature conversion , classification model "method = class "
```{r}
library(rattle)
```
```{r}
fancyRpartPlot(fit)
```

