---
title: "Regression analysis"
author: "H"
date: "10/23/2021"
output: html_document
---

```{r}
df <- read.csv('Marketing_Analysis_IBM.csv', header = TRUE, sep = ",")
```

```{r}
head(df, 10)
```

## Data analysis and visualization
## Encode Response data as intringer
```{r}
df$Engaged <- ifelse(df$Response == "Yes", 1, 0)
```
```{r}
head(df, 50)
```

## Engagement Rate 
```{r}
library(dplyr)
```
```{r} 
EngagementRate <- df %>% group_by(Engaged) %>% summarise(Count =n()) %>% mutate(Percentage = Count/nrow(df)*100)
```
```{r}
head(EngagementRate)
```
## Trabspose Data Frame
```{r}
transposed <- t(EngagementRate)
colnames(transposed) <- EngagementRate$Engaged
transposed <- transposed[-1,]
```

```{r}
head(transposed)
```
###  14% of marketing calls were responsed and 85% of call were not responsed

## Saes Channel 
```{r}
SalesChannel <- df %>% group_by(Engaged, Channel =Sales.Channel) %>% summarise(Count =n())
```
```{r}
head(SalesChannel)
```
## Pie Chart 
```{r}
library(ggplot2)
```
```{r}
ggplot(aes(x ="", y= Count, fill= Channel), data = SalesChannel) +geom_bar(width = 1, stat = "identity", position = position_fill()) +
  geom_text(aes(x= 1.25, label =Count), position = position_fill(vjust= 0.5))+ coord_polar("y") +facet_wrap(~ Engaged)+ ggtitle('Sales Channel (0:Not Engaged, 1: Engaged)') + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), plot.title = element_text(hjust = 0.5))
```
## Total Claim Amount
```{r}
ggplot(aes(x= "", y= Total.Claim.Amount), data = df) + geom_boxplot()+ facet_wrap(~Engaged) +ylab("Total Claim Amount") +xlab("0 :Not Engaged, 1:Engaged")+
  ggtitle("Engaged vs.Not Engaged: Total Claim Amount") +theme(plot.title = element_text(hjust = 0.5))
```
## Remove outlier 
```{r}
ggplot(aes(x= "", y= Total.Claim.Amount), data = df) + geom_boxplot(outlier.shape = NA)+scale_y_continuous(limits = quantile(df$Total.Claim.Amount,c(0.1,0.9)))+ facet_wrap(~Engaged) +ylab("Total Claim Amount") +xlab("0 :Not Engaged, 1:Engaged")+
  ggtitle("Engaged vs.Not Engaged: Total Claim Amount") +theme(plot.title = element_text(hjust = 0.5))
```

## Regression Analysis 
## Continuous Variables
## Get data types of each column
```{r}
sapply(df,class)
```
## summary statistics per columns
```{r}
summary(df)
```

## get numeric colums 
```{r}
continuosDF <- select_if(df,is.numeric)
```
```{r}
colnames(continuosDF)
```
##Fit regression model with continuos variables 
```{r}
logit.fit <- glm(Engaged ~ ., data = continuosDF, family = binomial)

```
```{r}
summary(logit.fit)

```
## p-value is less than 0.05 cut off line, the lower value is the stronger relationship 
## Income, Number.of.Policies,Total.Claim.Amount has 0.1 significant codes              
## z value - Income and Total.Claim.Amount has positive correlation, the more income and total claim amount, the more likely to engage marketing calls
## number of. policies has negative correaltion, the higher number of policies, the less engage marketing calls 

## Categorical Variable 
## a,. Education 
## Fit regression model with education factor 
```{r}
logit.fit <- glm(Engaged ~ factor (Education),data= df, family = binomial)

```

```{r}
summary(logit.fit)
```
## In this output there is no "Bachelor" category. It is included in Intercept 
### Intercept coefficient is negative, customers who have  Bachelor  less likely to engage marketing calls
### Doctor and Engaged has positive coefficent , higher educational customers , the more engage marketing calls

## Education +gender
### Fit regression model with education & Gender variable 
```{r}
logit.fit <-glm(Engaged ~factor(Education)+factor(Gender),family = binomial,data = df)
```

```{r}
summary(logit.fit)
```
### In this case we can only see Gender M, it is because of Female with Bachelor degree are in Intercept data 

## Combining Continuous and Categorical Variables 
```{r}
continuosDF$Gender <- factor(df$Gender)
continuosDF$Education <- factor(df$Education)
```
```{r}
colnames(continuosDF)
```
Fit regression model with Education & Gender variables 
```{r}
logit.fit <- glm(Engaged~ ., data = continuosDF, family = binomial)
```

```{r}
summary(logit.fit)
```
### Total.Claim.Amount and EducationDoctor variables have  significant  at 0.05 significant level and both have positive coefficient with Engaged.
### Income, Number.of.Policies ,  EducationMaster variable have significant relationships  at 0.1 significant level 
